A prototype software framework for transferable computational health economic models and its early application in youth mental health

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
cull

<!-- Import_start -->Computational models, particularly those addressing economic topics, have become essential tools for health policy development [@dakin2015influence; @Erdemir2020]. Although influential and widely used, health economic models can be skills and resource intensive to undertake.<!-- Import_end --> One suggestion for making health economic modelling projects more tractable is for health economists to re-use each other's models [@Arnold2010].

@@

<!-- End_Imported_from_Ethics -->A potential strategy for implementing transferable CHEMs is to adopt an open-source and modular approach to model development. Open source projects grant third parties liberal permissions to access, use and modify model source code and data.  Many health economists support greater use of open-source CHEMs as a means of improving model transparency, promoting model reuse, making model development more efficient and gaining the confidence of model users [@Pouwels2022]. A number of complex open source computational modelling projects in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust] have been implemented as modular models. A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular]. Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering]. Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular].

<!-- Modular CHEMs provide an opportunity for multiple modelling teams to contribute to, test and reuse models.  -->
<!-- @Jansen2019 -->
<!-- @thokala2023living LIVING HTA-->
<!-- https://www.ispor.org/publications/journals/value-outcomes-spotlight/vos-archives/issue/view/addressing-assessment-and-access-issues-for-rare-diseases/the-role-of-education-in-shaping-an-open-source-future -->
Actual implementations of open-source CHEMs are relatively rare [@Emerson2019; @Michalczyk2018; @Feenstra2022]. Recent efforts to build this field including an initiative to develop a suite of open source CHEMs addressing different health conditions in the United States [@Jansen2019] and a Canadian platform facilitating access to and validation of multiple CHEMs [@harvard2022developing]. Modular health economic models are also rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013]. Barriers to greater use of open-source approaches include health economist concerns about intellectual property, confidentiality, model misuse and the resources required to maintain open source implementations [@Pouwels2022; @Wu2019]. <!--Benefits --><!-- Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but  --><!-- Guidelines for implementing open source CHEMs remain scarce, piecemeal and need improving [@Sampson2019].  -->When health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit the reuse of models and their constituent code and data [@Feenstra2022]. Health econmists have also identified issues relating to model generalisability and transferability and model implementation software platforms as important barriers to open-source CHEMs [@Pouwels2022]. We are not aware of published literature identifying barriers to modular CHEMs, but potentially these may relate to the limited benefit of undertaking modular approaches in projects that are not also open-source.
<!-- Move to discussion--><!-- In health economics the related and enabling concept of reference models has been recommended [@Afzali2013].  -->
<!-- Transferring a health economic model developed for one jurisdiction for application in another typically involves retaining some features and updating others [@barbieri2010international]. However, models do not always make implementation choices (for example, use of concepts with standardised meanings across jurisdictions)<!-- [@garcia2021cost] -->  <!-- facilitate such selective re-use. -->
<!-- Open-source CHEMs remain rare [@Feenstra2022; @Emerson2019]. The software used to develop CHEMs was identified as a barrier to open-source model implementations by participants in a 2020 survey of health economists [@Pouwels2022]. Other reported barriers relate to difficulties in generalising models, updating models and transferring model data, concerns about the level of public access and lack of interest from decision-makers, and legal, confidentiality and security considerations [@Pouwels2022].  -->
<!-- typically have a number of limitations that at best restrict their usefulness and which in some cases may facilitate harmful misuse. -->

Some of the technical barriers<!-- Give examples --> to the development of transferable CHEMs that use open-source and modular approaches could be addressed by appropriate software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development]. A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs. Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software]. Software frameworks have widely been developed and implemented in data science, for example, PyTorch [@PyTorch2019] for machine learning using Python. However, software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software]. Software frameworks can also be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].

>>>>

<!-- Import_start -->Computational models, particularly those addressing economic topics, have become essential tools for health policy development [@dakin2015influence; @Erdemir2020]. Although influential and widely used, health economic models can be skills and resource intensive to develop.<!-- Import_end --> One suggestion for making health economic modelling projects more tractable is for health economists to re-use each other's models [@Arnold2010].

@@

<!-- End_Imported_from_Ethics -->
<!-- A potential strategy for implementing transferable CHEMs is to adopt an open-source and modular approach to model development. Open source projects grant third parties liberal permissions to access, use and modify model source code and data.  Potential benefits of open-source CHEMs that have been identified by health economists include improving model transparency, promoting model reuse, making model development more efficient and gaining the confidence of model users [@Pouwels2022]. A number of complex open source computational modelling projects in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust] have also been implemented as modular models. A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular]. Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering]. Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular].  -->

<!-- Modular CHEMs provide an opportunity for multiple modelling teams to contribute to, test and reuse models.  -->
<!-- @Jansen2019 -->
<!-- @thokala2023living LIVING HTA-->
<!-- https://www.ispor.org/publications/journals/value-outcomes-spotlight/vos-archives/issue/view/addressing-assessment-and-access-issues-for-rare-diseases/the-role-of-education-in-shaping-an-open-source-future -->
<!-- Actual implementations of open-source CHEMs are relatively rare [@Emerson2019; @Michalczyk2018; @Feenstra2022]. Recent efforts to build this field including an initiative to develop a suite of open source CHEMs addressing different health conditions in the United States [@Jansen2019] and a Canadian platform facilitating access to and validation of multiple CHEMs [@harvard2022developing]. Modular health economic models are also rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013]. Barriers to greater use of open-source approaches include health economist concerns about intellectual property, confidentiality, model misuse and the resources required to maintain open source implementations [@Pouwels2022; @Wu2019].  -->
<!--Benefits --><!-- Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but  --><!-- Guidelines for implementing open source CHEMs remain scarce, piecemeal and need improving [@Sampson2019].  -->
<!-- When health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit the reuse of models and their constituent code and data [@Feenstra2022]. Health economists have also identified issues relating to model generalisability and transferability and the software platforms in which CHEMs are authored as important barriers to open-source CHEMs [@Pouwels2022]. We are not aware of published literature identifying barriers to modular CHEMs, but potentially these may relate to the limited benefit of undertaking modular approaches in projects that are not also open-source. -->
<!-- Move to discussion--><!-- In health economics the related and enabling concept of reference models has been recommended [@Afzali2013].  -->
<!-- Transferring a health economic model developed for one jurisdiction for application in another typically involves retaining some features and updating others [@barbieri2010international]. However, models do not always make implementation choices (for example, use of concepts with standardised meanings across jurisdictions)<!-- [@garcia2021cost] -->  <!-- facilitate such selective re-use. -->
<!-- Open-source CHEMs remain rare [@Feenstra2022; @Emerson2019]. The software used to develop CHEMs was identified as a barrier to open-source model implementations by participants in a 2020 survey of health economists [@Pouwels2022]. Other reported barriers relate to difficulties in generalising models, updating models and transferring model data, concerns about the level of public access and lack of interest from decision-makers, and legal, confidentiality and security considerations [@Pouwels2022].  -->
<!-- typically have a number of limitations that at best restrict their usefulness and which in some cases may facilitate harmful misuse. -->

Some of the barriers<!-- Give examples --> to the development of transferable CHEMs <!-- that use open-source and modular approaches  -->could be addressed by appropriate software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development]. A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs. Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software]. Software frameworks have widely been developed and implemented in data science, for example, PyTorch [@PyTorch2019] for machine learning using Python. However, software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software]. Software frameworks can also be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
cull

---
title: "Predr_Cors"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r cpkgs, tab.cap='Software framework R libraries', tab.id = 'cpkgs', echo = F, results = 'asis'}
library(kableExtra)  
df <- tibble::tibble(Package = c("ready4",
                                       "ready4fun",
                                       "ready4class",
                                       "ready4pack",
                                       "ready4use",
                                       "ready4show"),
                     Purpose = c("Provide a template and novel syntax for modular CHEM implementations and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs.",
                                 "Streamline and standardise the authoring and documenting of functions that support transferable and generalisable model algorithms.",
                                 "Streamline and standardise the authoring and documenting of new interoperable CHEM modules.",
                                 "Help bundle and disseminate newly created CHEM modules as R libraries that are documented, licensed and quality assured.",
                                 "Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories.",
                                 "Facilitate the use of CHEM modules in programs to implement integrated and reproducible data ingest, analysis and reporting pipelines."),
                           # A = c("3","2-3","2","1-2,5,7","1-2,7","4,6"), 
                           # R = c("4","5","4-5","1,3,6","3,7",""),
                           # U = c("","","","1-3","1",""),
                           `R library dependencies` = Package %>%
                             purrr::map(~ {
                               utils::packageDescription(.x) %>%
                                 `[`(c("Depends", "Imports")) %>%
                                 purrr::map(~{
                                   if(is.null(.x)){
                                     character(0)
                                     }else{
                                       .x %>%
                                         strsplit(",\\n") %>%
                                         purrr::flatten_chr() %>%
                                         purrr::map(~strsplit(.x,", ") %>%
                                                      purrr::flatten_chr()) %>%
                                         purrr::flatten_chr() %>% sort() %>%
                                         purrr::discard(~startsWith(.x,"R "))
                                       }
                                   }) %>%
                                 purrr::flatten_chr() %>%
                                 unique() %>%
                                 sort() %>%
                                 purrr::map_chr(~{
                                   updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
                                   problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
                                     unname()
                                   if(!is.na(problem_idx_1L_chr))
                                     updated_1L_chr <- updated_1L_chr %>%
                                     stringr::str_sub(end = problem_idx_1L_chr-1)
                                   updated_1L_chr %>% 
                                     trimws(which = "left") 
                                   })
                               }) %>% 
                             purrr::map_chr (~ .x %>% paste0(collapse = " "))) %>% 
  as.data.frame() 
# if(params$X@outp_formats_chr[1] != "Word"){
#       df$Ref <- c(rep("",6)
#        # "@ready42022","@ready4fun2022","@ready4class2022","@ready4pack2022","@ready4use2022","@ready4show2022"
#                   )
# }else{
#   df$Ref <- ""
# }

@@

  dplyr::select(Package,
                #Ref,
                Purpose,
                #Standard,
                `R library dependencies`)

names_chr <- names(df)
# df <- data.frame(df[,1],
#                  rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;"),
#                      nrow(df)),
#                  df[,2#:3
#                     ],
#                  rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;")
#                      ,nrow(df)),
#                  #df[,4],
#                  #rep("&nbsp; &nbsp; &nbsp;",nrow(df)),
#                  df[,3#5
#                     ])
# colnames(df) <- c("Package",
#                   ifelse(params$X@outp_formats_chr[1] == "Word","XXX"," "),
#                   #"Ref", 
#                   "Purpose", 
#                   ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
#                   #"Standard     ",# " ",
#                   "R library dependencies")
#df$Package <- "![](../Data/images/ready4.png){ width=10% }"#"\\includegraphics[valign=T,scale=2.5,raise=2mm]{../Data/images/ready4.png}"
#df$`Standard     `  <- df$`Standard     ` %>% stringr::str_replace_all("&nbsp;"," ")
if(params$X@outp_formats_chr[1] == "Word") {
  library("flextable")
  library("ftExtra")
  df[,c(1,3:4,6:7)] %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
    ftExtra::colformat_md()
  }else{
    #df$Ref<-NULL
    #df$Package <- ""
    df$Package  <- df$Package %>% 
                      purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
    # df$Package <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"
    #df[,c(1,3,5:6)]   %>%
    df %>%
    # kableExtra::kbl(format = "markdown",
    #                   escape = F,
    #                 caption = knitr::opts_current$get("tab.cap"))
      kableExtra::kbl(booktabs = T, 
                      escape = F,
                      caption = knitr::opts_current$get("tab.cap")) %>%
      kableExtra::kable_paper(full_width = F) %>%
      kableExtra::column_spec(2, width = "20em", latex_valign = "m") %>%
      # kableExtra::column_spec(1, 
      #                         image = kableExtra::spec_image(rep("../Data/images/ready4.png",nrow(df)), 
      #                                                           150, 150)) %>%
      kableExtra::column_spec(3, width = "20em",
                              latex_valign = "m")
    }
```

>>>>

---
title: "Predr_Cors"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r cpkgs, tab.cap='Software framework R libraries', tab.id = 'cpkgs', echo = F, results = 'asis'}
library(kableExtra)  
df <- tibble::tibble(Library = c("ready4",
                                       "ready4fun",
                                       "ready4class",
                                       "ready4pack",
                                       "ready4use",
                                       "ready4show"),
                     Purpose = c("Provide a template and novel syntax for modular CHEM implementations and tools for finding interoperable CHEM modules, datasets and reproducible analysis programs.",
                                 "Streamline and standardise the authoring and documenting of functions that support transferable and generalisable model algorithms.",
                                 "Streamline and standardise the authoring and documenting of new interoperable CHEM modules.",
                                 "Help bundle and disseminate newly created CHEM modules as R libraries that are documented, licensed and quality assured.",
                                 "Help manage the labelling and transfer of data between CHEM modules and local and remote data repositories.",
                                 "Facilitate the use of CHEM modules in programs to implement integrated and reproducible data ingest, analysis and reporting pipelines."),
                           # A = c("3","2-3","2","1-2,5,7","1-2,7","4,6"), 
                           # R = c("4","5","4-5","1,3,6","3,7",""),
                           # U = c("","","","1-3","1",""),
                           `R library dependencies` = Library %>%
                             purrr::map(~ {
                               utils::packageDescription(.x) %>%
                                 `[`(c("Depends", "Imports")) %>%
                                 purrr::map(~{
                                   if(is.null(.x)){
                                     character(0)
                                     }else{
                                       .x %>%
                                         strsplit(",\\n") %>%
                                         purrr::flatten_chr() %>%
                                         purrr::map(~strsplit(.x,", ") %>%
                                                      purrr::flatten_chr()) %>%
                                         purrr::flatten_chr() %>% sort() %>%
                                         purrr::discard(~startsWith(.x,"R "))
                                       }
                                   }) %>%
                                 purrr::flatten_chr() %>%
                                 unique() %>%
                                 sort() %>%
                                 purrr::map_chr(~{
                                   updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
                                   problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
                                     unname()
                                   if(!is.na(problem_idx_1L_chr))
                                     updated_1L_chr <- updated_1L_chr %>%
                                     stringr::str_sub(end = problem_idx_1L_chr-1)
                                   updated_1L_chr %>% 
                                     trimws(which = "left") 
                                   })
                               }) %>% 
                             purrr::map_chr (~ .x %>% paste0(collapse = " "))) %>% 
  as.data.frame() 
# if(params$X@outp_formats_chr[1] != "Word"){
#       df$Ref <- c(rep("",6)
#        # "@ready42022","@ready4fun2022","@ready4class2022","@ready4pack2022","@ready4use2022","@ready4show2022"
#                   )
# }else{
#   df$Ref <- ""
# }

@@

  dplyr::select(Library,
                #Ref,
                Purpose,
                #Standard,
                `R library dependencies`)

names_chr <- names(df)
# df <- data.frame(df[,1],
#                  rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;"),
#                      nrow(df)),
#                  df[,2#:3
#                     ],
#                  rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp;")
#                      ,nrow(df)),
#                  #df[,4],
#                  #rep("&nbsp; &nbsp; &nbsp;",nrow(df)),
#                  df[,3#5
#                     ])
# colnames(df) <- c("Library",
#                   ifelse(params$X@outp_formats_chr[1] == "Word","XXX"," "),
#                   #"Ref", 
#                   "Purpose", 
#                   ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
#                   #"Standard     ",# " ",
#                   "R library dependencies")
#df$Library <- "![](../Data/images/ready4.png){ width=10% }"#"\\includegraphics[valign=T,scale=2.5,raise=2mm]{../Data/images/ready4.png}"
#df$`Standard     `  <- df$`Standard     ` %>% stringr::str_replace_all("&nbsp;"," ")
if(params$X@outp_formats_chr[1] == "Word") {
  library("flextable")
  library("ftExtra")
  df %>% #[,c(1,3:4,6:7)] %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
    ftExtra::colformat_md()
  }else{
    #df$Ref<-NULL
    #df$Library <- ""
    # df$Library  <- df$Library %>% 
    #                   purrr::map_chr(~paste0("\\includegraphics[valign=M,width=1.9cm,raise=4mm]{../Data/images/",.x,"_logo.png}"))#scale=0.4,raise=3mm]
    # df$Library <- "\\includegraphics[valign=M,scale=0.08,raise=3mm]{../Data/images/ready4.png}"
    #df[,c(1,3,5:6)]   %>%
    df %>%
    # kableExtra::kbl(format = "markdown",
    #                   escape = F,
    #                 caption = knitr::opts_current$get("tab.cap"))
      kableExtra::kbl(booktabs = T, 
                      escape = F,
                      caption = knitr::opts_current$get("tab.cap")) %>%
      kableExtra::kable_paper(full_width = F) %>%
      kableExtra::column_spec(2, width = "20em", latex_valign = "m") %>%
      # kableExtra::column_spec(1, 
      #                         image = kableExtra::spec_image(rep("../Data/images/ready4.png",nrow(df)), 
      #                                                           150, 150)) %>%
      kableExtra::column_spec(3, width = "20em",
                              latex_valign = "m")
    }
```

### 2024-02-27 Markdown/Manuscript/Child_RMDs/MS_Tables_3b.Rmd
cull

---
title: "Predr_Cors"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r rfwnlibs, tab.cap='readyforwhatsnext module libraries for utility mapping', tab.id = 'cpkgs', echo = F, results = 'asis'}
library(kableExtra)  
df <- tibble::tibble(Package = c("youthvars",
                                       "scorz",
                                       "specific",
                                       "TTU",
                                       "youthu"),
                     Purpose = c("Describe and validate youth mental health human record datasets.",
                                 "Score multi-attribute instruments.",
                                 "Construct and evaluate utility mapping models.",
                                 "Implement reproducible utility mapping sudies.",
                                 "Apply utility mapping models to out of sample data."),
                           `R library dependencies` = Package %>%
                             purrr::map(~ {
                               utils::packageDescription(.x) %>%
                                 `[`(c("Depends", "Imports")) %>%
                                 purrr::map(~{
                                   if(is.null(.x)){
                                     character(0)
                                     }else{
                                       .x %>%
                                         strsplit(",\\n") %>%
                                         purrr::flatten_chr() %>%
                                         purrr::map(~strsplit(.x,", ") %>%
                                                      purrr::flatten_chr()) %>%
                                         purrr::flatten_chr() %>% sort() %>%
                                         purrr::discard(~startsWith(.x,"R "))
                                       }
                                   }) %>%
                                 purrr::flatten_chr() %>%
                                 unique() %>%
                                 sort() %>%
                                 purrr::map_chr(~{
                                   updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
                                   problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
                                     unname()
                                   if(!is.na(problem_idx_1L_chr))
                                     updated_1L_chr <- updated_1L_chr %>%
                                     stringr::str_sub(end = problem_idx_1L_chr-1)
                                   updated_1L_chr %>% 
                                     trimws(which = "left") 
                                   })
                               }) %>% 
                             purrr::map_chr (~ .x %>% paste0(collapse = " "))) %>% 
  as.data.frame() 
df <- df %>%
  dplyr::select(Package,
                Purpose,
                `R library dependencies`)

>>>>

---
title: "Predr_Cors"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r rfwnlibs, tab.cap='Model module libraries for utility mapping', tab.id = 'cpkgs', echo = F, results = 'asis'}
library(kableExtra)  
df <- tibble::tibble(Library = c("youthvars",
                                       "scorz",
                                       "specific",
                                       "TTU",
                                       "youthu"),
                     Purpose = c("Describe and validate youth mental health human record datasets.",
                                 "Score multi-attribute instruments.",
                                 "Construct and evaluate utility mapping models.",
                                 "Implement reproducible utility mapping sudies.",
                                 "Apply utility mapping models to out of sample data."),
                           `R library dependencies` = Library %>%
                             purrr::map(~ {
                               utils::packageDescription(.x) %>%
                                 `[`(c("Depends", "Imports")) %>%
                                 purrr::map(~{
                                   if(is.null(.x)){
                                     character(0)
                                     }else{
                                       .x %>%
                                         strsplit(",\\n") %>%
                                         purrr::flatten_chr() %>%
                                         purrr::map(~strsplit(.x,", ") %>%
                                                      purrr::flatten_chr()) %>%
                                         purrr::flatten_chr() %>% sort() %>%
                                         purrr::discard(~startsWith(.x,"R "))
                                       }
                                   }) %>%
                                 purrr::flatten_chr() %>%
                                 unique() %>%
                                 sort() %>%
                                 purrr::map_chr(~{
                                   updated_1L_chr <- stringr::str_replace_all(.x,"\\n"," ")
                                   problem_idx_1L_chr <- stringr::str_locate(updated_1L_chr," ")[1,1] %>%
                                     unname()
                                   if(!is.na(problem_idx_1L_chr))
                                     updated_1L_chr <- updated_1L_chr %>%
                                     stringr::str_sub(end = problem_idx_1L_chr-1)
                                   updated_1L_chr %>% 
                                     trimws(which = "left") 
                                   })
                               }) %>% 
                             purrr::map_chr (~ .x %>% paste0(collapse = " "))) %>% 
  as.data.frame() 
df <- df %>%
  dplyr::select(Library,
                Purpose,
                `R library dependencies`)

### 2024-02-27 Markdown/Manuscript/Parent_PDF/Springer.Rmd
cull

  - firstname: David  
    lastname: Baker
    #     email: david.baker@orygen.org.au
    affiliation: [2,3]

@@

affiliations:
  - number: 1
    corresponding: TRUE
    info:
      orgdiv: School of Public Health and Preventive Medicine
      orgname: Monash University
    address:
        #street: "553 St Kilda Road"
        city: Melbourne
        #postcode: 3004
        #state: Victoria
        country: Australia
  - number: 2
    corresponding: FALSE
    info:
      orgname: Orygen
    address:
     #   street: "35 Poplar Road"
        city: Parkville
        # postcode: 3052
        #state: Victoria
        country: Australia
  - number: 3
    corresponding: FALSE
    info:
      orgdiv: Centre for Youth Mental Health
      orgname: The University of Melbourne
    address:
     #   street: "35 Poplar Road"
        city: Parkville
        # postcode: 3052
    #   state: Victoria
        country: Australia
  - number: 4
    corresponding: FALSE
    info:
#      orgdiv: XXXXXXXXXXX
      orgname: Heart Foundation      
    address:
     #   street: "2/850 Collins St"
        city: Docklands
        # postcode: 3008
     #   state: Victoria
        country: Australia
  - number: 5
    corresponding: FALSE
    info:
#      orgdiv: XXXXXXXXXXX
      orgname: headspace National Youth Mental Health Foundation   
    address:
    #  #   street: "485 La Trobe St"
        city: Melbourne
    #     postcode: 3000
    #  #   state: Victoria
        country: Australia     
  - number: 6
    corresponding: FALSE
    info:
      orgdiv: Institute for Health and Sport
      orgname: Victoria University 
    address:
    #  #   street: "70/104 Ballarat Rd"
        city: Footscray
    #     postcode: 3011
    #  #   state: Victoria
        country: Australia 
      # 
  - number: 7
    corresponding: FALSE
    info:
#      orgdiv: XXXXXXXXXXX
      orgname: Flinders University   
    address:
    #     # street: "182 Victoria Square"     
        city: Adelaide
    #     postcode: 5000
    #  #   state: South Australia
        country: Australia 
keywords:  
  - computational models
  - ethics of modelling
  - health economics
  - mental disorders
  - open-source models
  - software frameworks

>>>>

  - firstname: David  
    particle: G
    lastname: Baker
    #     email: david.baker@orygen.org.au
    affiliation: [2,3]

@@

affiliations:
  - number: 1
    corresponding: TRUE
    info:
      orgdiv: School of Public Health and Preventive Medicine
      orgname: Monash University
    address:
        #street: "553 St Kilda Road"
        city: Melbourne
        #postcode: 3004
        #state: Victoria
        country: Australia
  - number: 2
    corresponding: FALSE
    info:
      orgname: Orygen
    address:
     #   street: "35 Poplar Road"
        city: Parkville
        # postcode: 3052
        #state: Victoria
        country: Australia
  - number: 3
    corresponding: FALSE
    info:
      orgdiv: Centre for Youth Mental Health
      orgname: The University of Melbourne
    address:
     #   street: "35 Poplar Road"
        city: Parkville
        # postcode: 3052
    #   state: Victoria
        country: Australia
  - number: 4
    corresponding: FALSE
    info:
#      orgdiv: XXXXXXXXXXX
      orgname: Heart Foundation      
    address:
     #   street: "2/850 Collins St"
        city: Docklands
        # postcode: 3008
     #   state: Victoria
        country: Australia
  - number: 5
    corresponding: FALSE
    info:
#      orgdiv: XXXXXXXXXXX
      orgname: headspace National Youth Mental Health Foundation   
    address:
    #  #   street: "485 La Trobe St"
        city: Melbourne
    #     postcode: 3000
    #  #   state: Victoria
        country: Australia     
  - number: 6
    corresponding: FALSE
    info:
      orgdiv: Institute for Health and Sport
      orgname: Victoria University 
    address:
    #  #   street: "70/104 Ballarat Rd"
        city: Footscray
    #     postcode: 3011
    #  #   state: Victoria
        country: Australia 
      # 
  - number: 7
    corresponding: FALSE
    info:
#      orgdiv: XXXXXXXXXXX
      orgname: Flinders University   
    address:
    #     # street: "182 Victoria Square"     
        city: Adelaide
    #     postcode: 5000
    #  #   state: South Australia
        country: Australia 
keywords:  
  - adolescence
  - computational models
  - health economics
  - mental disorders
  - open-source models
  - software frameworks
